Nail: A practical interface generator for data formats

### 2014-04-30 paper/osdi14/design.tex
Design and related work

\paragraph{Semantic Bijecction.}
Second, this well-defined internal representation allows Nail to invert the
parser and generate output, while maintaining a \emph{semantic bijection}, that is, when generating
the corresponding output to a parser input, the two byte streams will have the same meaning, i.e. be
interpreted the same by Nail, but might not be identical.
A bijection in the traditional sense often does not make sense when parsing data formats. 
Consider a grammar for a text language that tolerates white space, or a binary protocol that tolerates
arbitrarily long padding.\footnote{Say, the physical layer of most communication
  protocols is a possibly infinite sequence of symbols that are syntactically
  nil followed by a pre-determined synchronization sequence and the actual
  contents of the transmission.} Program semantics should be
independent of the number of padding elements in the input, and Nail therefore
does not expose that information to the programmer. We call such discarded
fields \emph{constants}. 
Similarly, Nail does not preserve the layout of
objects referred to by their offsets. If the grammar consists of a simple protocol without offset
fields, constants and the like, there is a normal bijection between the internal model and valid
parser inputs.
\paragraph{Hide redundant information.}
Nail's internal model is designed to hide unneeded information from the application. The more
information Nail automatically deduces, the less the application can produce invalid data.
Therefore, Nail introduces \emph{dependent fields}, which contain data that can be computed during
generation and needs to be kept as additional state during parsing.

@@

We will introduce transformations, which allow the programmer to write arbitrary functions that can
handle such structures and streams, which are a generic abstraction for input and output data that
allow the decoded data to be integrated with the rest of the generated Nail parser.

>>>>

\paragraph{Semantic Bijecction.}
Second, in order to generate output, Nail maintaining
a \emph{semantic bijection} between the external format and the internal model. That is, when
generating the corresponding output to a parser input, the two byte streams will have the same
meaning, i.e. be interpreted the same by Nail, but might not be identical.
 A bijection in the traditional sense often does not make sense for data
formats. Consider a grammar for a text language that tolerates white space, or a binary protocol
that tolerates arbitrarily long padding.
%\footnote{Say, the physical layer of most communication
%  protocols is a possibly infinite sequence of symbols that are syntactically nil followed by a
%  pre-determined synchronization sequence and the actual contents of the transmission.}
 Program semantics should be independent of the number of padding elements in the input, and Nail therefore
does not expose that information to the programmer. We call such discarded fields \emph{constants}.
Similarly, Nail does not preserve the layout of objects referred to by their offsets. If the grammar
consists of a simple protocol without offset fields, constants and the like, there is a conventional
bijection between  internal models and valid parser inputs.
\paragraph{Hide redundant information.}
Nail's internal model is designed to hide unneeded and redundant information from the application.
Nail introduces \emph{dependent fields}, which contain data that can be computed during generation
and needs to be kept as additional state during parsing. Dependent fields are for example used to represent
lengths, offsets and checksums.

@@

Nail introduce transformations, which allow the programmer to write arbitrary functions that can
handle such structures and streams, which are a generic abstraction for input and output data that
allow the decoded data to be integrated with the rest of the generated Nail parser.

### 2014-04-30 paper/osdi14/relwk.tex
Design and related work

% A subclass of logic errors are so-called \textit{weird machines}, where
% implementation side effects or under-specified parser behavior leads to a
% protocol or data format inadvertently becoming a Turing-complete execution
% environment, even though the original grammar did not require it.
% Frequently, this execution environment can either
% then directly manipulate data in unwanted ways or be used to make
% exploiting another bug feasible.\footnote{For example, by compiling a
% return-oriented-programming exploit from code fragments discovered on
% the fly.} Examples include x86 page tables~\cite{bangert2013page}, and
% ELF symbols and relocations~\cite{shapiro2013weird}. In the offensive
% research community, this has been generalized into treating a program
% as a \textit{weird machine}~\cite{bratus2011exploit} that operates on
% an input, analogous to a virtual machine operating on bytecode.
% Nail avoids these problems by having the parser precisely match the
% specified grammar, eliminating under-specified behavior.

@@

Proper input recognition has  been shown to be an excellent way of
eliminating ambiguous inputs. In one case, a  PDF parser implemented in
Coq could eliminate over $95\%$ of known malicious PDFs~\cite{Bogk-PDF}.
However, manually writing parser code does not scale to the number of
file formats  and protocols in existence and might result in parser code
tied to one specific application.

>>>>

% A subclass of logic errors are so-called \textit{weird machines}, where
% implementation side effects or under-specified parser behavior leads to a
% protocol or data format inadvertently becoming a Turing-complete execution
% environment, even though the original grammar did not require it.
% Frequently, this execution environment can either
% then directly manipulate data in unwanted ways or be used to make
% exploiting another bug feasible.\footnote{For example, by compiling a
% return-oriented-programming exploit from code fragments discoverepd on
% the fly.} Examples include x86 page tables~\cite{bangert2013page}, and
% ELF symbols and relocations~\cite{shapiro2013weird}. In the offensive
% research community, this has been generalized into treating a program
% as a \textit{weird machine}~\cite{bratus2011exploit} that operates on
% an input, analogous to a virtual machine operating on bytecode.
% Nail avoids these problems by having the parser precisely match the
% specified grammar, eliminating under-specified behavior.

@@

Proper input recognition has been shown to be an excellent way of eliminating ambiguous inputs. In
one case, a PDF parser implemented in Coq could eliminate over $95\%$ of known malicious
PDFs~\cite{Bogk-PDF}. The same project also produced a ``counter-example'' PDF that triggered
numerous bugs in other PDF parsers. However, manually writing parser code and proving unambiguity
does not scale to the number of file formats and protocols in existence and might result in parser
code tied to one specific application.
